\documentclass[a4paper, 12pt, twppages]{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{eso-pic}
\usepackage{fancyhdr}
\usepackage{pdfpages}
\usepackage{hyperref}
\usepackage{cleveref}

\begin{document}
\pagebreak

\thispagestyle{fancy}


{\vspace{2cm}~}
{\vspace{2cm}}

{\noindent\large Project Paper}
\vspace{1cm}

{\noindent\huge\textbf{Using a Random Forest for Static Analysis of Android Malware}}

\bigskip

{\noindent\LARGE Group 2}


\bigskip
{\vspace{2cm}}
{\noindent\large {\bf Supervisor:} Nils Löhndorf}

\bigskip

%% WRITE THE DATAE OF SUBMISSION
{\noindent\large {\bf Date of Submission:} 26. January 2018}

\bigskip\bigskip\bigskip\bigskip\bigskip\bigskip

{\em\noindent Department of Information Systems and Operations, Vienna University of
Economics and Business, Welthandelsplatz 1, 1020 Vienna, Austria
}


\pagestyle{empty}
\pagebreak
\tableofcontents
\pagebreak
\listoftables
\pagebreak


\begin{abstract}
Malware is a constant threat to users of the Android operating system. In regions where Google Play is not used as application distributor, malware increasingly exceeds benignware. We try to solve this problem by using Machine Learning algorithms to automatically detect either benign or malicious intents of Android applications. This way, users could more easily be notified of previously unknown malware. We use the Drebin dataset \cite{drebin} four our classifier. It includes around 120.000 benignware and 6.000 malware samples. We train various Machine Learning algorithms on the Drebin dataset and show that the Random Forest algorithm surpasses the performance of the SVM used in \cite{drebin}, reaching a true positive rate of 95 \% and a false positive rate of 0.6 \%. We also were provided with a newer dataset with proper class balance by IKARUS Security Software GmbH, but could not finish our analysis on it due to time constraints.
\end{abstract}

\pagebreak

\input{paper.tex}



\bibliographystyle{plain}
\bibliography{references}

\end{document}
